Estimation of flow trajectories in a multi-lines transportation network

### 2023-02-21 latex_files/applied_network_science_article/article_v0.tex
write article

Note that, by construction, the mean margin error should be null when the algorithm converges. However, it can be informative to track down this error along iterations and, in some practical cases where the network is large, the algorithm convergence criterion is reached without having margin constraints perfectly respected.

@@

\subsubsection{Examples construction}
\label{example_construction}

@@

First, we shows some algorithm iterations on a toy example with $p=2$, where $100$ passengers where drawn uniformly across the $\vert P \vert = 20$ possible $st$-trips. Some iterations of the algorithm with $\theta=0.1$, along with MTE and MME errors, are shown in Figure \ref{iteration_plots}. 
\begin{figure}[h]
	\label{iteration_plots}
	\includegraphics[width=0.98\textwidth]{fig/iterations.pdf}
	\caption{Real transportation flow (green arrows) obtained by randomly drawing $100$ passengers on the graph toy example with $p=2$ line tours, along with iterations $1, 3, 6, 10, 15$ of the algorithm with $\theta=0.1$. MTE and MME errors are computed, and embarkment and disembarkment flows are represented respectively by the red and blue colors on nodes.}
\end{figure}
On this small example, we can see that the algorithm quickly find an estimation giving small MME error, but still give an MTE of 0.252. This result is due to the fact that only $100$ passengers are drawn, giving a large deviation compared to the optimally found solution which maximize the entropy. Interestingly, we see that a better result is found on iteration 6, but margins constraints at this point are not perfectly respected yet.

>>>>

Note that, by construction, the MME should be null when the algorithm converges. However, it can be informative to track down this error along iterations and, in some practical cases where the network is large, the algorithm convergence criterion is reached without having margin constraints perfectly respected.

@@

\subsubsection{Construction}
\label{example_construction}

@@

First, we shows some algorithm iterations on a toy example with $p=2$, where $100$ passengers where drawn uniformly across the $\vert P \vert = 20$ possible $st$-trips. Some iterations of the algorithm with $\theta=0.1$, along with MTE and MME errors, are shown in Figure \ref{iteration_plots}. 
\begin{figure}[h]
	\includegraphics[width=0.98\textwidth]{fig/iterations.pdf}
	\caption{Real transportation flow (green arrows) obtained by randomly drawing $100$ passengers on the graph toy example with $p=2$ line tours, along with iterations $1, 3, 6, 10, 15$ of the algorithm with $\theta=0.1$. MTE and MME errors are computed, and embarkment and disembarkment flows are represented respectively by the red and blue colors on nodes.}
	\label{iteration_plots}
\end{figure}
On this small example, we can see that the algorithm quickly find an estimation giving small MME error, but still give an MTE of 0.252. This result is due to the fact that only $100$ passengers are drawn, giving a large deviation compared to the optimally found solution which maximize the entropy. Interestingly, we see that a better result is found on iteration 6, but margins constraints at this point are not perfectly respected yet.

\subsubsection{MTE study}
\label{mte_study}

The main goal of toy examples, since we have access to the real transportation flow, is to study how the resulting $MTE$ behave regarding passenger $st$-trips distribution and hyperparameter $\theta$ on different network sizes.
